{\LARGE Model Selection for Scalar-on-Function Regression \\ with Applications to Near-Infrared Spectroscopy}

### 2022-02-01 Paper/main.tex
3.6 KL

	\begin{equation}\label{CovarianceFunction}
		c(t,s) = \mathbb{E}\big[ \left( X(\omega)(t) - \mu(t) \right) \left( X(\omega)(s) - \mu(s) \right) \big]
	\end{equation}
	{\color{orange}suggestion from here}
	where the $c(t,s)$ are Hilbert-Shmidt Kernels defined through c : $[0,1] \times [0,1] \rightarrow \mathbb{R}$. Let $K$ be the integral operater on $\mathbb{L}^{2}[0,1]$ such that $K : \nu \rightarrow K \nu$ for $\nu \in \mathbb{L}^{2}[0,1]$, by
	\begin{equation}
		[K \nu](t) = \int_{0}^{1}c(t,s) \nu(s)ds
	\end{equation}

	Then, the operator $K$ has orthonormal basis functions $\nu_{i} \in \mathbb{L}^{2}[0,1]$ corresponding to eigenvalues $\lambda_{i}$ for all $i$ since it is a positive compact self-adjoint operator. Moreover, $K$ holds following traits:

		\begin{enumerate}
			\item The eigenspaces corresponding to distinct eigenvalues are mutually orthogonal.
			\item The eigenspaces corresponding to non-zero eigenvalues are finite-dimentsional.
			\item The eigenvalues can be ordered in nonincreasing order as follows $\lambda_{1} \geq \lambda_{2} \geq \dots \geq 0$.
		\end{enumerate}

	Therefore, we can approximate the function $X$ with first few eigenfunctions. The functions $X$ are approximated enough well by first few principal components since the order of them are sorted in descending order (e.g. $Var(\xi_{j}) \geq Var(\xi_{k})$ for all $j > k$). Theoretical considerations lead to the result that $X$ can be represented in the following form, called its Karhunen-Lo\'{e}ve expansion. {\color{orange} The proofs are provided at \ref{Proof1} and \ref{Proof2}.}

@@

	where the $\nu_j$ are defined by the countable set of solutions $\{(\lambda^m, \nu^m) \: \vert \: m \in \mathbb{N}\}$ of the following equation.

@@

	The $\xi_j(\omega)$ are then given as 
	\begin{equation}
		\xi^m(\omega) = \langle X(\omega) - \mu, \nu^m\rangle = \int_{0}^{1} \left(X(\omega)(s) - \mu(s)\right) \nu^m(s) \mathrm{d}s
	\end{equation} 
	and thereby random variables realizing in $\mathbb{R}$ and have the following properties akin to $\Lambda^{\frac{1}{2}} D(\omega)$ for the case of a random vector. {\color{orange} We would need to assume that the process is centered, otherwise we may not derive below results(not sure though).}

	\begin{multicols}{2}
		\begin{enumerate}
			\item $\mathbb{E}\left[\xi_j(\omega)\right] = 0$
			\item $Var\left(\xi_j(\omega)\right) = \lambda_i$
			\item $Cov\left(\xi_j(\omega), \xi_k(\omega)\right) = 0$ if $j \neq k$
		\end{enumerate}
	\end{multicols}

@@

	\begin{equation}
		x_i(t) = \hat{\mu}(t) + \sum_{j = 1}^{{\color{red} !!!}} \hat{\xi}_{i,j} \hat{\nu}(t)
	\end{equation}
	where the $\hat{\xi}_{i}^m$ are derived as

>>>>

	\begin{equation}\label{CovarianceFunction}
		c(t,s) = \mathbb{E}\big[ \left( X(\omega)(t) - \mu(t) \right) \left( X(\omega)(s) - \mu(s) \right) \big]
	\end{equation}
	where the $c(t,s)$ are Hilbert-Shmidt Kernels defined through $c : [0,1] \times [0,1] \rightarrow \mathbb{R}$. Let $K$ be the integral operater on $\mathbb{L}^{2}[0,1]$ such that $K : \nu \rightarrow K \nu$ for $\nu \in \mathbb{L}^{2}[0,1]$, by
	\begin{equation}
		[K \nu](t) = \int_{0}^{1}c(t,s) \nu(s)ds
	\end{equation}

	Then, the operator $K$ has orthonormal basis functions $\nu_{i} \in \mathbb{L}^{2}[0,1]$ corresponding to eigenvalues $\lambda_{i}$ for all $i$ since it is a positive compact self-adjoint operator. Moreover, $K$ holds that the eigenvalues can be ordered in nonincreasing order as follows $\lambda^{1} \geq \lambda^{2} \geq \dots \geq 0$ where the superscript is not the power but index. Therefore, the functions $X$ are approximated enough well by first few principal components since the order of them are sorted in descending order of eigenvalues corresponding to the eigenfunctions (e.g. $Var(\xi^{m}) \geq Var(\xi^{n})$ for all $m > n$). Theoretical considerations lead to the result that $X$ can be represented in the following form, called its Karhunen-Lo\'{e}ve expansion.

	%\begin{enumerate}
	%\item The eigenspaces corresponding to distinct eigenvalues are mutually orthogonal.
	%\item The eigenspaces corresponding to non-zero eigenvalues are finite-dimentsional.
	%\item The eigenvalues can be ordered in nonincreasing order as follows $\lambda_{1} \geq \lambda_{2} \geq \dots \geq 0$.
	%\end{enumerate}
	%Therefore, the functions $X$ are approximated enough well by first few principal components since the order of them are sorted in descending order of eigenvalues corresponding to the eigenfunctions (e.g. $Var(\xi_{j}) \geq Var(\xi_{k})$ for all $j > k$). Theoretical considerations lead to the result that $X$ can be represented in the following form, called its Karhunen-Lo\'{e}ve expansion. {\color{orange} The proofs are provided at \ref{Proof1} and \ref{Proof2}.}

@@

	where the $\nu_j$ are defined by the countable set of solutions $\{(\lambda^m, \nu^m) \: \vert \: m \in \mathbb{N}\}$ of the following equation. The proofs are provided at \ref{Proof1} and \ref{Proof2}.

@@

	The $\xi_j(\omega)$ are then given as 
	\begin{equation}
		\xi^m(\omega) = \langle X(\omega) - \mu, \nu^m\rangle = \int_{0}^{1} \left(X(\omega)(s) - \mu(s)\right) \nu^m(s) \mathrm{d}s
	\end{equation} 
	and thereby random variables realizing in $\mathbb{R}$ and have the following properties akin to $\Lambda^{\frac{1}{2}} D(\omega)$ for the case of a random vector.

	\begin{multicols}{2}
		\begin{enumerate}
			\item $\mathbb{E}\left[\xi^m(\omega)\right] = 0$
			\item $Var\left(\xi^m(\omega)\right) = \lambda^m$
			\item $Cov\left(\xi^m(\omega), \xi^n(\omega)\right) = 0$ if $m \neq n$
		\end{enumerate}
	\end{multicols}

@@

	\begin{equation}
		x_i(t) = \hat{\mu}(t) + \sum_{j = 1}^{{\color{red} !!!}} \hat{\xi}_{i}^{m} \hat{\nu}^{m}(t)
	\end{equation}
	where the $\hat{\xi}_{i}^m$ are derived as
